\hspace*{0.7in}Understanding the need for managing BigData, a wide study is done of NoSQL Databases. Among which Oracle NoSQL Database was selected and it came into focus that, the Oracle NoSQL database is a fine tool to fulfill our needs, but Oracle NoSQL does not provide simplicity for naïve users to utilize it. So this project is developed to manage the Oracle NoSQL Database by providing Graphical User Interface and Web Services to utilize the Oracle NoSQL facilities.
\\\hspace*{0.7in}The Project concentrates on Graphical User Interface to Manage the Key Value Pairs on Oracle NoSQL Database. The GUI developed in this project provides all the functions to manage the Oracle NoSQL Database. The System provides all CRUD operations and Import CSV and Export Data Facility. The System uses Disconnected Architecture.
\\\hspace*{0.7in}Further, RESTFul Web Services are developed which can be accessed from any platform. An Attendance Check application is developed for Android Platform, which demonstrates the use of Oracle NoSQL for managing Big Data. Here the BigData is taken as Sensor Data generated from Bio Metrics Thumb machine.
\\\hspace*{0.7in}The Future Scope includes developing a complete package of Web Services to use Oracle NoSQL Database.
\\\hspace*{0.7in}So, "A Tool for Managing Key Value Pairs on Oracle NoSQL Database" will definitely help all the users of Oracle NoSQL Database to utilize its all functionalities. And will encourage scholars to further study and develop the application.
